### 2025-04-21 thesis/thesis.tex
Update

\usepackage[a4paper]{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{float}
\usepackage{hyperref}
\usepackage{titlesec}

@@

\begin{titlepage}
    \begin{center}
        \begin{Large}
            Brandenburg University of Technology \\[1em]
        \end{Large}
        IT Security \\
        Computerscience and Media \\
        Prof. Dr. Oleg Lobachev \\
        Florian Eich
    \end{center}

@@

    \begin{center}
        \Large{Natural Language Queries using Large Language Models}\\[0.5em]
        \large{Bachelor Thesis}\\[1em]

@@

Test\cite{Atlas}

\subsection{360 Degree vergleichbare paper etc.}

@@

\subsection{Integration of the GPT Model}
\subsubsection{Model Selection and Optimization}
\subsubsection{API Connection or Local Embedding}

\subsection{Development of the PostgreSQL Extension}
\subsubsection{SQL Functions for GPT Interactions}
\subsubsection{Data Type Conversion and Processing}
\subsubsection{Error Handling and Logging}

\subsection{Optimization}
\subsubsection{Performance Tuning}
\subsubsection{Memory Usage}
\subsubsection{Parallelization}

@@

\bibliographystyle{apalike}
\bibliography{references}

>>>>

\usepackage[a4paper]{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{float}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage[natbibapa]{apacite}

@@

\begin{titlepage}
    \begin{center}
        \begin{Large}
            Brandenburg University of Applied Sciences \\[1em]
        \end{Large}
        IT Security \\
        Computerscience \\
        Prof. Dr. Oleg Lobachev \\
        MSc. Florian Eich
    \end{center}

@@

    \begin{center}
        \Large{A Natural Language Interface Implementation for PostgreSQL using LLMs, Self-Correction and Incremental Schema Analysis}\\[0.5em]
        \large{Bachelor Thesis}\\[1em]

@@

Test\citep{Atlas}

@@

\subsection{Integration of the Model}

\subsection{Development of the PostgreSQL Extension}

\subsection{Optimization}

@@

\bibliographystyle{apacite}
\bibliography{references}
